A fast unified model for parsing and sentence understanding

### 2016-03-18 writing/hard_stack_paper/paper.tex
Tiny typos

We compare our models against several baselines, including the strongest published non-neural network-based result from \citet{snli:emnlp2015} and previous neural network models built around several types of sentence encoder.

@@

Both SPINN-PI and the full SPINN outperform all previous sentence encoding models by a significant margin. Most notably our modes outperform the Tree-based CNN of \citet{mou2015recognizing}, which also uses tree-structured composition for local feature extraction, but uses simpler pooling techniques to build sentence features in the interest of efficiency. Our results show that a model that uses tree-structured composition fully (SPINN) outperforms one which uses it only partially (Tree-based CNN), which in turn outperforms one which does not use it at all (LSTM RNN).

>>>>

We compare our models against several baselines, including the strongest published non-neural network-based result from \citet{snli:emnlp2015} and previous neural network models built around several types of sentence encoders.

@@

Both SPINN-PI and the full SPINN outperform all previous sentence encoding models by a significant margin. Most notably our models outperform the Tree-based CNN of \citet{mou2015recognizing}, which also uses tree-structured composition for local feature extraction, but uses simpler pooling techniques to build sentence features in the interest of efficiency. Our results show that a model that uses tree-structured composition fully (SPINN) outperforms one which uses it only partially (Tree-based CNN), which in turn outperforms one which does not use it at all (LSTM RNN).
